---
title: "GovResearchTesting"
output: html_document
date: "2025-04-07"
---




NOTE: if you are getting a glitch when it comes to loading the data, try switching the read.table function to the one that has file.choose(). 



```{r}

library(readr)
library(dplyr)
library(tidyverse)


#data <- read.table("file.choose()", header = TRUE, sep = ",")
data <- read.table("sub-data.txt", header = TRUE, sep = ",")


colnames(data) <- c("ID_3", "Party_ID_withMore", "Gaureenteeed_Job_Income", "Gov_Spending", "Assistance_to_Blacks", "EnviorBuissTradeOff", "DefenseSpending", "HealthCare")


#I'm pretty sure this works 
recodedData <- data %>% 
  mutate(Gov_Spending = case_when( 
    Gov_Spending == 1 ~ 7, # recodes GovSpending so that 1 is liberal and 7 is conservative
    Gov_Spending == 2 ~ 6, 
    Gov_Spending == 3 ~ 5, 
    Gov_Spending == 4 ~ 4, 
    Gov_Spending == 5 ~ 3, 
    Gov_Spending == 6 ~ 2, 
    Gov_Spending == 7 ~ 1
    )) %>% 
  filter(ID_3 %in% c(1,2,3)) %>%  #includes only repuvlica, democrat, and independant
  filter(Party_ID_withMore %in% c(1,2,3,4,5,6,7)) %>% #These will include only the 1-7 coded vars 
  filter(Gaureenteeed_Job_Income %in% c(1,2,3,4,5,6,7)) %>% 
  filter(Gov_Spending %in% c(1,2,3,4,5,6,7)) %>% 
  filter(Assistance_to_Blacks %in% c(1,2,3,4,5,6,7)) %>% 
  filter(EnviorBuissTradeOff %in% c(1,2,3,4,5,6,7)) %>% 
  filter(DefenseSpending %in% c(1,2,3,4,5,6,7)) %>% 
  filter(HealthCare %in% c(1,2,3,4,5,6,7)) 

#From here on out, only use the "recodedData" object. 

str(recodedData)
head(recodedData)


```


Starting the data analysis:

To do: 
 
 1. create a column that has the sum of all the independant variables that we're using 
 
 2. then group by those columnsn, 
 
 3. summarise to find the mean. 
 
 4. go from there: 
 
 
 
  
```{r}

#this will add a new column that is the sum of all of our factors columns:
recodedData <- recodedData %>% 
  mutate(PartisianSum = ID_3 + Party_ID_withMore + Gaureenteeed_Job_Income + Gov_Spending + Assistance_to_Blacks + EnviorBuissTradeOff + DefenseSpending + HealthCare)

head(recodedData)



```
 

We find that the mean of the "PartisianSum" column is: 30.68238 (on a scale of 6 to 42). Double check if this is right
```{r}
mean(recodedData$PartisianSum)
```
 
 
 
 
 
 
 
 
 
 

