---
title: "GovResearchTesting"
output: html_document
date: "2025-04-07"
---






```{r}

library(readr)
library(dplyr)
library(tidyverse)


data <- read.table(file.choose(), header = TRUE, sep = ",")
#data <- read.table("sub-data.txt", header = TRUE, sep = ",")


colnames(data) <- c("ID_3", "Party_ID_withMore", "Gaureenteeed_Job_Income", "Gov_Spending", "Assistance_to_Blacks", "EnviorBuissTradeOff", "DefenseSpending", "HealthCare")


#I'm pretty sure this works 
recodedData <- data %>% 
  mutate(Gov_Spending = case_when( 
    Gov_Spending == 1 ~ 7, # recodes GovSpending so that 1 is liberal and 7 is conservative
    Gov_Spending == 2 ~ 6, 
    Gov_Spending == 3 ~ 5, 
    Gov_Spending == 4 ~ 4, 
    Gov_Spending == 5 ~ 3, 
    Gov_Spending == 6 ~ 2, 
    Gov_Spending == 7 ~ 1
    )) %>% 
  filter(ID_3 %in% c(1,2,3)) %>%  #includes only repuvlica, democrat, and independant
  filter(Party_ID_withMore %in% c(1,2,3,4,5,6,7)) %>% #These will include only the 1-7 coded vars 
  filter(Gaureenteeed_Job_Income %in% c(1,2,3,4,5,6,7)) %>% 
  filter(Gov_Spending %in% c(1,2,3,4,5,6,7)) %>% 
  filter(Assistance_to_Blacks %in% c(1,2,3,4,5,6,7)) %>% 
  filter(EnviorBuissTradeOff %in% c(1,2,3,4,5,6,7)) %>% 
  filter(DefenseSpending %in% c(1,2,3,4,5,6,7)) %>% 
  filter(HealthCare %in% c(1,2,3,4,5,6,7)) 

#From here on out, only use the "recodedData" object. 

str(recodedData)
head(recodedData)


```


Starting the data analysis:

To do: 
 
 1. create a column that has the sum of all the independant variables that we're using 
 
 2. then group by those columnsn, 
 
 3. summarise to find the mean. 
 
 4. go from there: 
 
 
 
  
```{r}

#this will add a new column that is the sum of all of our factors columns:
recodedData <- recodedData %>% 
  mutate(PartisianSum = ID_3 + Party_ID_withMore + Gaureenteeed_Job_Income + Gov_Spending + Assistance_to_Blacks + EnviorBuissTradeOff + DefenseSpending + HealthCare)

head(recodedData)



```
 

We find that the mean of the "PartisianSum" column is: 28.26746 (on a scale of 6 to 42). Double check if this is right, it changed randomly at some point idk what I did 
```{r}
mean(recodedData$PartisianSum)
```
 
 
 Testing if different groups have different means: 
 
1 is Democrat
2 is Republican
3 is Independent
```{r}
recodedData %>% 
  group_by(ID_3)%>% 
  summarize(
            NumberOfRespondants = n(),
            MeanPartisianShip = mean(PartisianSum))
```
 
 
 
 Next to do: 

  try this on the other party ID variable that has more variations (like democrat, slightly democrat, very democrat, etc), and see if that makes a differenc ein the data.  
 
 
              1  1. Strong Democrat
               2  2. Not very strong Democrat
               3  3. Independent-Democrat
               4  4. Independent
               5  5. Independent-Republican
               6  6. Not very strong Republican
               7  7. Strong Republican
               
```{r}
recodedData <- recodedData %>% 
  mutate(Party_ID_withMore = case_when(
    Party_ID_withMore == 1 ~ "Strong Democrat",
    Party_ID_withMore == 2 ~ "Not very strong Democrat",
     Party_ID_withMore == 3 ~ "Independent-Democrat",
      Party_ID_withMore == 4 ~ "Independent",
       Party_ID_withMore == 5 ~ "Independent-Republican",
        Party_ID_withMore == 6 ~ "Not very strong Republican",
         Party_ID_withMore == 7 ~ "Strong Republican"
  )) %>% mutate(Party_ID_withMore = factor(Party_ID_withMore, 
                                    levels = c("Strong Democrat", "Not very strong Democrat", 
                                               "Independent-Democrat", "Independent", 
                                               "Independent-Republican", 
                                               "Not very strong Republican", 
                                               "Strong Republican"))) 


recodedData %>% 
  group_by(Party_ID_withMore) %>% 
  summarize( 
    MeanPartisianShip = mean(PartisianSum), 
    NumOfRespondants = n()
    )



```

 
 

